The Social Conditioning of Fear

### 2023-12-07 scripts/manuscript.qmd
try commit final draft

---
title: "The Social Conditioning of Fear"
author:
  - Alejandra Pedraza
  - W. Jamie Yang
abstract: "Fear at night has been perceived as a form of gender-based violence with sexual assault implications. However, this more insidious and everyday forms of harassment are frequently not captured by common survey instruments. In this study, we investigate the inequalities in terms of fear of walking alone at night among the US adult population and mapping out the patterns of disparities along the axes of race, gender, sexual orientation, citizenship status, and education. We use the 2022 data from the General Social Survey (GSS) and the data science tools from EDLD 651 class to delineate the data distribution and basic correlations between fear of walking alone at night and our other variables of interest. Our findings suggest that fear at night differs by race, gender, subjective health, and neighborhood diversity. Consistent with previous research, women were also more likely than men to report fear at night. Importantly, groups with multiply marginalized social identities are likely to report higher rates of fear at night." # this is where abstract should be pasted 
format: html
wordcount-html: default
toc: true
toc-location: left
toc-title: Table of Contents
highlight-style: pygments
editor: visual
execute:
  eval: false # change to false before final submission
  echo: true
  message: false
  warning: false
fig-width: 6.5
fig-height: 8
code-fold: true
code-summary: "View Code"
embed-resources: true
bibliography: references.bib
link-citations: true
---

>>>>

---
title: "The Social Conditioning of Fear"
author:
  - Alejandra Pedraza
  - W. Jamie Yang
abstract: "Fear at night has been perceived as a form of gender-based violence with sexual assault implications. However, this more insidious and everyday forms of harassment are frequently not captured by common survey instruments. In this study, we investigate the inequalities in terms of fear of walking alone at night among the US adult population and mapping out the patterns of disparities along the axes of race, gender, sexual orientation, citizenship status, and education. We use the 2022 data from the General Social Survey (GSS) and the data science tools from EDLD 651 class to delineate the data distribution and basic correlations between fear of walking alone at night and our other variables of interest. Our findings suggest that fear at night differs by race, gender, subjective health, and neighborhood diversity. Consistent with previous research, women were also more likely than men to report fear at night. Importantly, groups with multiply marginalized social identities are likely to report higher rates of fear at night." # this is where abstract should be pasted 
format: html
wordcount-html: default
toc: true
toc-location: left
toc-title: Table of Contents
highlight-style: pygments
editor: visual
execute:
  eval: true # change to false before final submission
  echo: true
  message: false
  warning: false
fig-width: 6.5
fig-height: 8
code-fold: true
code-summary: "View Code"
embed-resources: true
bibliography: references.bib
link-citations: true
---
